Simple Wind Models

### 2010-07-16 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5051 ac11df5e-a788-c23b-a8e1-c758c323924d

@@

Table~\ref{tab:line_diag} presents a series of quantitative measures
for the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
the fiducial model and a set of the variations.  Listed are the
equivalent wdiths (absorption and emission), the peak optical depth
for the absorption $\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the
velocity where the optical depth peaks $v_\tau$, the optical
depth-weighted velocity centroid $v_{\bar \tau} \equiv \int dv v
\ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in
emission, the velocity where the flux peaks $v_f$, and the
flux-weighted velocity centroid of the emission line $v_{\bar f}$.

One observes a wide range in these measures.  This emphasize the
challenge in converting the absorption/emission data to physical
constraints on wind schenarios.  We return to further consider these
results in $\S$~\ref{sec:obs}.

@@

The models investigated in the previous two sections
assumed power-law descriptions for both the density and velocity
expressions of the wind (Equations~\ref{eqn:density},\ref{eqn:vel}).
The power-law exponents were arbitrarily chosen, with minimal physical
motivation.  In this sub-section, we explore the results for a series
of other power-law expressions.

@@

@@

@@

The Lyman break galaxies (LBGs), UV color-selected galaxies at $z \sim 3$,
exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
etc.\ transitions with speeds up to 1000\kms\
\citep[e.g.][]{lkg+97,pks+98,steidel+10}.
Researchers have invoked these winds to explain enrichment of
the intergalactic medium \citep[e.g.][]{aguirre,spa+06}, the origin of the
damped \lya\ systems \citep{nbf98,schaye01a}, and XXX.  Although the
presence of these outflows were established over a decade ago,
the processes that drive them remain
unidentified.  Similarly,  current estimates of the mass and energetics of the
outflow suffer from orders of magnitude uncertainty.

Recently, \cite[][; hereafter S10]{steidel+10} introduced a model to
explain jointly the average absorption they observed
toward a set of several hundred LBGs and the average absorption in cool gas
observed transverse to these galaxies.  
Their wind model is defined by two
expressions: (i) a radial velocity law $\mvr(r)$ and (ii) the covering
fraction of optically thick gas $f_c(r)$.  For the latter, S10
envision an 
ensemble of small, optically thick clouds $(\tau \gg 1)$ that only
partially cover the galaxy.
For the velocity law, they adopted the following functional
form

@@

The covering fraction of optically thick cold gas, meanwhile, was assumed to have
the functional form

@@

In the following, we consider two methods to analyze the LBG wind.
Both approaches assume isotropy and adopt the velocity law given by
Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
diffuse medium with unit convering fraction and a radial density
profile determined from the Sobolev approximation.  We then apply 
the methodology used for the other wind models.  In the other model,
we modify our algorithms to more precisely mimic the concept of an
ensemble of optically thick clouds with a partial covering fraction.

@@

We verified that the density profile shown in
Figure~\ref{fig:LBG_Sobolev}a
reproduces the proper
absorption profile by discretizing the gas into a series of layers
and calculating the integrated absorption profile.  This
calculation is shown as a dotted red curve in
Figure~\ref{fig:LBG_Sobolev}b which is an excellent
match to the desired profile (black curve).
To calculate the optical depth profiles for the other transitions, we
assume $\mnfe = \mnmg/2$ and scale $\tau$ by $f\lambda$.

We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
using the 1D algorithm with no dust extinction; these are shown as
red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
should focus on the \mgiia\ transition.  The dotted line in the Figure
shows the intensity profile for the model when one ignores re-emission
of absorbed photons.  By construction, it follows\footnote{Note that
  one should not make this comparison for the other transitions in
  this Sobolev model because those are scaled down by $f\lambda$ and
  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} the profile
described by Equation~\ref{eqn:LBG_I} as plotted in
Figure~\ref{fig:LBG_Sobolev}b.   In comparison, the full model (solid,
red curve)
shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$
due to scattered photons.
In this respect, our LBG-Sobolev model is an
inaccurate description of the observations. The model
also predicts significant emission in the \ion{Mg}{2} lines and several of
the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
has been observed for \ion{Si}{2}$^*$
transitions in LBGs \citep{prs+02,shapley03}, but
the \ion{Fe}{2}$^*$ transitions
modeled here lie in the near-IR and have not yet been investigated.
On the other hand, there have been no 
reported detections of significant line-emission related to resonance
transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
\citep{wcp+09,rubin09}.  
The principal result is that the scattering and re-emission of
absorbed photons signficantly alters the predicted absorption profiles
for the inputted model.  This is, of course, an unavoidable
consequence of an isotropic, dust-free model with unit covering
fraction.
[Transition?]

[Do CIV scattered photons bugger up the P-Cygni analysis of Pettini
et al. ?]

@@

In the previous sub-section, we described a Sobolev solution that
reproduces the average absorption profile of LBGs in cool gas
transitions where scattered photons are ignored.  A proper analysis of
this wind model, however, predicts line profiles that are qualitatively
different from the ones observed because scattered photons fill-in
absorption and generate significant line emission (similar to the
fiducial wind model; $\S$~\ref{sec:fiducial}).
The LBG-Sobolev model, however, differs from
the one proposed by S10:  they proposed an ensemble of optically
thick clouds with the (parital) covering fraction described by
Equation~\ref{eqn:covering} whereas the Sobolev model assumes
a diffuse medium with a declining density profile but a unit covering
fraction.  At face value, one questions whether this difference leads to
the contradictory results of the model.

@@

The results of the full calculation (absorption plus scattering) are
shown as the black curve in Figure~\ref{fig:LBG_spec}.  The results
are very similar to the Sobolev calculation; scattered photons fill-in
the absorption profiles at $v \approx 0 \mkms$ and yield significant
emission lines at $v \gtrsim 0 \mkms$ in the resonance lines and at
all velocities for the \ion{Fe}{2}$^*$ transitions.  For \feiia,
the majority of absorbed photons have been converted to its
fine-structure counterparts lending to very weak emission at this
transition. The absorption profile very nearly matches the
model without re-emission indicating that this transition well
reproduces the opacity of the wind.  
The equivalent width of \feiia\ even exceeds that for \feiib, an
inversion that if observed would strongly support this model.
[Could SiII or OI do the same?]

Comparing the LBG Sobolev and parital covering models in
Figure~\ref{fig:LBG_spec} (via \mgiia), we note nearly identical
results.  The differencs that occur for the other transitions,
meanwhile, are only because their opacities are scaled downward in the
Sobolev model (as required).  [Do the data prefer one to the other?
And what if we modified the density away from Sobolev?]
In principle, they provide a means to distinguish between the two LBG
models.

@@

Given the essentially perfect correspondence between the Sobolev and
partical covering models (for \mgiia), we are motivated to consider
further the characteristics of the Sobolev model which offers a
density profile.  It is straightforward to convert the density and
velocity profiles into distributions of mass, energy, and momentum in
the wind.  These are shown in cumulative form in
Figure~\ref{fig:LBG_cumul}.  Before discussing the results, we offer
two cautionary comments: (i) the conversion of \nmg\ to $n_{\rm H}$
assumes a very poorly constrained scalar factor of $10^{5.7}$.  One
should give minimal weight to the absolute values for any of the
quantities;
(ii) the Sobolev approximation is not a proper description of the S10
LBG wind model.

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/energy_levels.ps}
\caption{
Energy level diagrams for the \mgiid\ doublet and the UV1
multiplet of \ion{Fe}{2} transitions   
(based on Figure~7 from \cite{hmt+99}).
Each transition shown is
labelled by its rest wavelength (\AA) and Einstein A-coefficient
(s$^{-1}$). Black upward arrows
indicate the resonance-line transitions, i.e.\ those connected to the ground
state.  The 2p$^6$3p configuration of Mg$^+$ is split into
two energy levels that give rise to the \mgiid\ doublet.  
Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
exhibit fine-structure splitting that gives rise to a series of
electric-dipole transitions. 
The downward (green) arrows show the transitions that are connected to the
resonance-line transitions (i.e.\ they share the same upper energy
levels).  We also show a pair of levels (\ion{Fe}{2}~$\lambda\lambda
2618,2631$) that arise from higher levels in the \zconfig\
configuration.  These transitions have not yet been observed in
galactic-scale outflows and are not considered in our analysis.
}
\label{fig:energy}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_nvtau_vs_r.ps}
\caption{
Density (dashed; red), radial velocity (dotted; blue), and
\mgiia\ optical depth profiles (solid; black) for the fiducial
wind model (see Table~\ref{tab:fiducial} for details).
The density and velocity laws are simple $r^{-2}$ and $r^1$
power-laws.  The optical depth profile was calculated by summing
the opacity at small and discrete radial intervals in velocity space
and then converted to radius with the velocity law.  One notes that
the wind is optically thick at the inner radius ($r_{\rm inner} =
1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
  outer} = 20$\,kpc).
Note that the density and velocity curves have been scaled for plotting
convenience.  
}
\label{fig:fiducial_nvt}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6,angle=90]{Figures/fig_fiducial_1d.ps}
\caption{
{\it Left} -- (Upper) \mgiid\ profiles for the fiducial wind model
described in Table~\ref{tab:fiducial} and
Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
characteritic of an outflow with significant absorption blueward of
line-center (dashed vertical lines) extending to $v = -1000\mkms$
and significant emission redward of line-center.  Note
that even though the peak optical depth of the \ion{Mg}{2} transitions
is nearly 30 at $v \approx -70 \mkms$, photons scattered off the outflow
fill in the absorption.
(Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
show weaker absorption due to the smaller Fe$^+$ number density and
lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
the emission for \feiia\ is significantly weaker than that of the
\feiib\ and \mgiid\ transitions.  This is because a majority of the
absorbed \feiia\ photons are converted into
\ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
{\it Right} -- A subset of the transitions displayed in a velocity
plot.
}
\label{fig:fiducial_1d}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_noemiss.ps}
\caption{
The solid curves show the line profiles (absorption and emission) of
the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
model.  These include the effects of scattered photons and show the
canonical P-Cygni profiles of a source 
embedded within an outflow.  Overplotted (dotted line) on each transition is
the predicted absorption profile under the constraint that every
absorbed photon is lost from the system, i.e.\ no scattering or
re-emission occurs.   These profiles have been `filled
in' significantly by light scattered in the wind.  Ignoring this
process, one would model the absorption lines with a systematically lower
optical depth and (incorrectly) conclude that the source is partly covered by the
gas.  It is essential, therefore, to account for the effects of
scattered/re-emitted photons in a proper analysis of the absorption
profiles of cool gas outflows.
}
\label{fig:noemiss}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_mgii.ps}
\caption{
Surface-brightness emission maps around the \mgiia\ transition for the
source+wind complex of the fiducial model.  The middel panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
curves indicate the velocity slices for the emission maps.  The
source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
pixels at the center.   At $v=-250 \mkms$, the wind has an optical
depth of $\tau_{2796} \approx 1$ and the source contributes
roughly half of the observed flux.  At $v=-100 \mkms$ the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  Impressively, this
emission exceeds the integrated flux at $v = -250\mkms$. At $v \ge 0
\mkms$,  both the source and wind contribute to the observed emission.
At all velocities, the majority of emission comes from the inner
$\approx 5$\,kpc.
}
\label{fig:fiducial_ifu_mgii}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_feii2600.ps}
\plotone{Figures/fig_fiducial_ifu_feii2612.ps}
\caption{
(a) Surface-brightness emission maps around the \feiib\ transition for the
source+wind complex.  The middle panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
curves indicating the velocity slices for the emission maps.  
The results are very similar to those observed for the \mgiid\ doublet
(Figure~\ref{fig:fiducial_ifu_mgii}).
(b) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
2612$ transition for the 
source+wind complex.  The middle panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
curves indicating the velocity slices for the emission maps.  
In this case, the source is unattenuated yet scattered photons from
the wind also have a significant contribution. 
}
\label{fig:fiducial_ifu_feii}
\end{figure}

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_asymm_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
case (black lines) compared against an anisotropic wind blowing into
only $2\pi$ steradians as viewed from $\theta = 0^\circ$ (source
uncovered) to $\theta = 180^\circ$ (source covered).  One detects
significant emission for all orientations of this wind. The velocity
centroid of this 
emission shifts from positive to negative velocities as $\theta$
increases.  The absorption reaches a maximum at $\theta > 100^\circ$
and disappears for $\theta = 0^\circ$.
}
\label{fig:anisotropic}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_dust_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
model (black) against a series of models that include the effects of
dust extinction parameterized by \taud.  The primary difference is the suppression of line
emission relative to the continuum (again, normalized to unit value).
A more subtle but important effect is that the redder photons in the
emission lines (corresponding to higher velocity relative to
line-center) suffer greater extinction.  This is most evident in the
\feiic\ emission line and occurs because these photons must
travel further to scatter off the backside of the wind.  Note that
the absorption lines are nearly unmodified until $\mtaud = 10$, a
level of extinction that would preclude observing the source
altogether.
}
\label{fig:dust}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_ism_diagn.ps}
\caption{
Density (dashed; red), radial velocity (dotted; blue), and
\mgiia\ optical depth profiles (solid; black) for the ISM+wind
model.  The wind is identical to the fiducial model
(Figure~\ref{fig:fiducial_nvt}) but this model also includes an ISM component
with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
\mkms$ and a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
Note that the density and velocity curves have been scaled for plotting
convenience.  
}
\label{fig:ISM}
\end{figure}

>>>>

[Do dust too (as a green curve in Figure~\ref{fig:ISM_spec})]

\subsection{Varying $n_{\rm H}^0$}

[Consider a series of models with the optical depth varying]

@@

Table~\ref{tab:line_diag} presents a series of quantitative measures
for the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
the fiducial model ($\S$~\ref{sec:fiducial}) and a set of the models
presented in this section.  Listed are the
equivalent widths (absorption and emission), the peak optical depth
for the absorption $\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the
velocity where the optical depth peaks $v_\tau$, the optical
depth-weighted velocity centroid $v_{\bar \tau} \equiv \int dv \, v
\ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in
emission, the velocity where the flux peaks $v_f$, and the
flux-weighted velocity centroid of the emission line $v_{\bar f}$.

One observes a wide range in these measures.  This emphasizes the
challenges to convert 1D spectra to physical
constraints on wind scenarios.  We consider these
results further in $\S$~\ref{sec:obs}.

@@

The models investigated in the previous two sections
assumed power-law descriptions for both the density and velocity
expressions of the wind (Equations~\ref{eqn:density},\ref{eqn:vel}).
The power-law exponents were arbitrarily chosen, with minimal physical
motivation.  In this sub-section, we explore the results for a series
of other power-law expressions.
We consider three different density laws ($n_{\rm H}(r) \propto
r^{-3}, r^{0}, r^2$) and three different velocity laws ($\mvr(r)
\propto r^{-2}, r^{-1}, r^{0.5}$) for 9 new wind models
(Table~\ref{tab:plaws}, Figure~\ref{fig:plaws}a).  [Comment in the Table how $\mvr$ is
different when the velocity law is positive]  
The density and velocity normalizations $n_{\rm H}^0, v^0$ have been
modified to yield an \mgiia\ optical depth profile that peaks at
$\tau_{2796}^{\rm max} \approx 10-10^3$ that usually decreases to
$\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b).

[Discuss models]

[Refer to Table~\ref{tab:plaw_diag}]

@@

[Kate: Write the details of velocity + density law]

@@

Figure~\ref{fig:rad_nvt}, \ref{fig:rad_spec}

@@

The Lyman break galaxies (LBGs), UV color-selected galaxies at $z \sim 3$,
exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
etc.\ transitions with speeds up to 1000\,\kms\
\citep[e.g.][]{lkg+97,pks+98}.
Researchers have invoked these winds to explain enrichment of
the intergalactic medium \citep[e.g.][]{aguirre,spa+06}, the origin of the
damped \lya\ systems \citep{nbf98,schaye01a}, and XXX.  Although the
presence of these outflows were established over a decade ago,
the processes that drive them remain
unidentified.  Similarly,  current estimates of the mass and energetics of the
outflow suffer from orders of magnitude uncertainty.

Recently, \cite[][; hereafter S10]{steidel+10} introduced a model to
explain jointly the average absorption they observed
toward a set of several hundred LBGs and the average absorption in gas
observed transverse to these galaxies.  
Their wind model is defined by two
expressions: (i) a radial velocity law $\mvr(r)$ and (ii) the covering
fraction of optically thick `clouds' $f_c(r)$.  For the latter, S10
envision an 
ensemble of small, optically thick $(\tau \gg 1)$ clouds that only
partially cover a galactic-scale source (i.e.\ a few to 10\,kpc).
For the velocity law, they adopted the following functional
form

@@

The covering fraction of optically thick clouds, meanwhile, was assumed to have
the functional form

@@

In the following, we consider two methods to analyze the LBG wind.
Both approaches assume isotropy and adopt the velocity law given by
Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
diffuse medium with unit convering fraction and a radial density
profile determined from the Sobolev approximation.  We then apply 
the Monte Carlo methodology used for the other wind models to predict
\ion{Mg}{2} and \ion{Fe}{2} line profiles.  In the other model,
we modify our algorithms to more precisely mimic the concept of an
ensemble of optically thick clouds with a partial covering fraction on
galactic scales.

@@

We verified that the density profile shown in
Figure~\ref{fig:LBG_Sobolev}a
reproduces the proper
absorption profile by discretizing the gas into a series of layers
and calculating the integrated absorption profile.  This
calculation is shown as a dotted red curve in
Figure~\ref{fig:LBG_Sobolev}b; it is an excellent
match to the desired profile (black curve).
To calculate the optical depth profiles for the other transitions, we
assume $\mnfe = \mnmg/2$ and scale $\tau$ by the $f\lambda$ product.

We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
using the 1D algorithm with no dust extinction; these are shown as
red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
should focus on the \mgiia\ transition.  The dotted line in the Figure
shows the intensity profile when one ignores re-emission
of absorbed photons.  By construction, it follows\footnote{Note that
  one should not make this comparison for the other transitions in
  the Sobolev model because those are scaled down by $f\lambda$ and
  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} the profile
described by Equation~\ref{eqn:LBG_I} as plotted in
Figure~\ref{fig:LBG_Sobolev}b.   In comparison, the full model (solid,
red curve)
shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$
due to scattered photons.
In this respect, our LBG-Sobolev model is an
inaccurate description of the observations. The model
also predicts significant emission in the \ion{Mg}{2} lines and several of
the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
has been observed for \ion{Si}{2}$^*$
transitions in LBGs \citep{prs+02,shapley03}, but
the \ion{Fe}{2}$^*$ transitions
modeled here lie in the near-IR and have not yet been investigated.
On the other hand, there have been no 
reported detections of significant line-emission related to resonance
transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
\citep{wcp+09,rubin09}.  
The principal result is that the scattering and re-emission of
absorbed photons signficantly alters the predicted absorption profiles
for the inputted model.  This is, of course, an unavoidable
consequence of an isotropic, dust-free model with unit covering
fraction.
[Transition?]

[Do CIV scattered photons bugger up the P-Cygni analysis of Pettini
et al. ? I bet they do!]

@@

In the previous sub-section, we described a Sobolev solution that
reproduces the average absorption profile of LBGs in cool gas
transitions where scattered photons are ignored.  A proper analysis of
this wind model, however, predicts line profiles that are qualitatively
different from the ones observed because scattered photons fill-in
absorption and generate significant line emission (similar to the
fiducial wind model; $\S$~\ref{sec:fiducial}).
The LBG-Sobolev model, however, differs from
the one proposed by S10:  these authors proposed an ensemble of optically
thick clouds with the (parital) covering fraction described by
Equation~\ref{eqn:covering} whereas the Sobolev model assumes
a diffuse medium with a declining density profile but a unit covering
fraction.  At face value, one questions whether this difference leads to
the contradictory results of the model.

@@

The results of the full calculation (absorption plus scattering) are
shown as the black curve in Figure~\ref{fig:LBG_spec}.  The results
are very similar to the Sobolev calculation; scattered photons fill-in
the absorption profiles at $v \approx 0 \mkms$ and yield significant
emission lines at $v \gtrsim 0 \mkms$ in the resonance
lines. Furthermore, significant emission is observed at
all velocities for the \feiis\ transitions.  For \feiia,
the majority of absorbed photons have been converted to its
fine-structure counterparts lending to very weak emission at this
transition. The absorption profile very nearly matches the
model without re-emission indicating that this transition well
reproduces the opacity of the wind.  
The equivalent width of \feiia\ even exceeds that for \feiib, an
inversion that, if observed, would strongly support this model.
[Could SiII or OI do the same?]

Comparing the LBG Sobolev and parital covering models in
Figure~\ref{fig:LBG_spec} (via \mgiia), we note nearly identical
results.  The differences that occur for the other transitions,
meanwhile, are only because the opacities are scaled downward in the
Sobolev model (as required).  [Do the data prefer one to the other?
And what if we modified the density away from Sobolev?]
In principle, they provide a means to distinguish between the two LBG
models.

@@

Given the essentially perfect correspondence between the Sobolev and
partical covering models (for \mgiia), we are motivated to consider
further the characteristics of the Sobolev model which has the
distinct advantage of producing a 
density profile.  It is straightforward, then, to convert the density and
velocity profiles into distributions of mass, energy, and momentum
within
the wind.  These are shown in cumulative form in
Figure~\ref{fig:LBG_cumul}.  Before discussing the results, we offer
two cautionary comments: (i) the conversion of \nmg\ to $n_{\rm H}$
assumes a very poorly constrained scalar factor of $10^{5.47}$.  One
should give minimal weight to the absolute values for any of the
quantities;
(ii) the Sobolev approximation is not a proper description of the S10
LBG wind model.

@@

\begin{figure}
\epsscale{0.95}
\plotone{Figures/energy_levels.ps}
\caption{
Energy level diagrams for the \mgiid\ doublet and the UV1
multiplet of \ion{Fe}{2} transitions   
(based on Figure~7 from \cite{hmt+99}).
Each transition shown is
labelled by its rest wavelength (\AA) and Einstein A-coefficient
(s$^{-1}$). Black upward arrows
indicate the resonance-line transitions, i.e.\ those connected to the ground
state.  The 2p$^6$3p configuration of Mg$^+$ is split into
two energy levels that give rise to the \mgiid\ doublet.  
Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
exhibit fine-structure splitting that gives rise to a series of
electric-dipole transitions. 
The downward (green) arrows show the \feiis\ transitions that are connected to the
resonance-line transitions (i.e.\ they share the same upper energy
levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
2618,2631$) that arise from higher levels in the \zconfig\
configuration.  These transitions have not yet been observed in
galactic-scale outflows and are not considered in our analysis.
}
\label{fig:energy}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_nvtau_vs_r.ps}
\caption{
Density (dashed; red), radial velocity (dotted; blue), and
\mgiia\ optical depth profiles (solid; black) for the fiducial
wind model (see Table~\ref{tab:fiducial} for details).
The density and velocity laws are simple $r^{-2}$ and $r^1$
power-laws.  The optical depth profile was calculated by summing
the opacity at small and discrete radial intervals in velocity space
and was then converted to radius with the velocity law.  One notes that
the wind is optically thick at the inner radius ($r_{\rm inner} =
1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
  outer} = 20$\,kpc).
Note that the density and velocity curves have been scaled for plotting
convenience.  
}
\label{fig:fiducial_nvt}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6,angle=90]{Figures/fig_fiducial_1d.ps}
\caption{
{\it Left} -- (Upper) \mgiid\ profiles for the fiducial wind model
described in Table~\ref{tab:fiducial} and
Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
characteritic of an outflow with significant absorption blueward of
line-center (dashed vertical lines) extending to $v = -1000\mkms$
and significant emission redward of line-center.  Note
that even though the peak optical depth of the \ion{Mg}{2} transitions
is $\tau_{2796}^{\rm max} \approx 30$ at $v \approx -70 \mkms$,
photons scattered off the outflow fill in the absorption.
(Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
show weaker absorption due to the smaller Fe$^+$ number density and
lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
the emission for \feiia\ is significantly weaker than that of the
\feiib\ and \mgiid\ transitions.  This is because a majority of the
absorbed \feiia\ photons are converted into
\ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
{\it Right} -- A subset of the transitions displayed in a velocity
plot.
}
\label{fig:fiducial_1d}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_noemiss.ps}
\caption{
The solid curves show the line profiles (absorption and emission) of
the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
model.  These include the effects of scattered photons and show the
canonical P-Cygni profiles of a source 
embedded within an outflow.  Overplotted (dotted line) on each transition is
the predicted absorption profile under the constraint that every
absorbed photon is lost from the system, i.e.\ no scattering or
re-emission occurs.   The true profiles have been `filled
in' significantly by light scattered in the wind.  Ignoring this
process, one would model the absorption lines with a systematically lower
optical depth and (incorrectly) conclude that the source is partly covered by the
gas.  
}
\label{fig:noemiss}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fiducial_ifu_mgii.ps}
\caption{
Surface-brightness emission maps around the \mgiia\ transition for the
source+wind complex of the fiducial model.  The middel panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
curves indicate the velocity slices for the emission maps.  The
source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
pixels at the center.   At $v=-250 \mkms$, the wind has an optical
depth of $\tau_{2796} \approx 1$ and the source contributes
roughly half of the observed flux.  At $v=-100 \mkms$ the
wind absorbs all photons from the source and the observed emission is
entirely due to photons scattered by the wind.  Impressively, this
emission exceeds the integrated flux at $v = -250\mkms$ such that the
line center is offset from the peak optical depth.  At $v \ge 0
\mkms$,  both the source and wind contribute to the observed emission.
At all velocities, the majority of emission comes from the inner
$\approx 5$\,kpc.
}
\label{fig:fiducial_ifu_mgii}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_feii_ifu.ps}
\caption{
(Upper) Surface-brightness emission maps around the \feiib\ transition for the
source+wind complex.  The middle panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
curves indicating the velocity slices for the emission maps.  
The results are very similar to those observed for the \mgiid\ doublet
(Figure~\ref{fig:fiducial_ifu_mgii}).
(Lower) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
2612$ transition for the 
source+wind complex.  The middle panel shows the 1D spectrum with $v=0
\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
curves indicating the velocity slices for the emission maps.  
In this case, the source is unattenuated yet scattered photons from
the wind also have a significant contribution. 
}
\label{fig:fiducial_ifu_feii}
\end{figure}

@@

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_asymm_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
case (black lines) compared against an anisotropic wind blowing into
only $2\pi$ steradians as viewed from $\theta = 0^\circ$ (source
uncovered) to $\theta = 180^\circ$ (source covered).  One detects
significant emission for all orientations of this wind but significant
absorption only for $\theta \ge 90^\circ$.
The velocity centroid of the 
emission shifts from positive to negative velocities as $\theta$
increases and one transitions from viewing the wind to be behind the
source to in front.  The velocity centroid of emission, therefore, may
give a robust measure of wind isotropy.
}
\label{fig:anisotropic}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_dust_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
model (black) against a series of models that include 
dust extinction.  The primary effect is suppression of
the line-emission relative to the continuum. 
A more subtle but important effect is that the redder photons in the
emission lines (corresponding to higher velocity relative to
line-center) suffer greater extinction.  This is most evident in the
\feiic\ emission line; it occurs because these photons must
travel farther to scatter off the backside of the wind.  Note that
the absorption lines are nearly unmodified until $\mtaud = 10$, a
level of extinction that would preclude observing the source
altogether.
}
\label{fig:dust}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_ism_diagn.ps}
\caption{
Density (dashed; red), radial velocity (dotted; blue), and
\mgiia\ optical depth profiles (solid; black) for the ISM+wind
model.  The wind is identical to that from the fiducial model
(Figure~\ref{fig:fiducial_nvt}) but this ISM+wind model also includes an ISM component
with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
\mkms$ and a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
Note that the density and velocity curves have been scaled for plotting
convenience.  
}
\label{fig:ISM}
\end{figure}

\begin{figure}
\epsscale{0.7}
\plotone{Figures/fig_ism_spec.ps}
\caption{
Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the ISM+wind
model (red) compared against the fiducial wind model (black). 
The dotted line traces the predicted absorption profile in the absence
of re-emission and scattering.
Regarding the \ion{Mg}{2}~doublet, the primary difference between the
ISM+wind and the fiducial models is the shift of $\approx 100 \mkms$
in the emission lines from $v \approx 0 \mkms$ for the fiducial
model to $v \approx +100\mkms$ for the ISM+wind model. 
For the ISM+wind model, 
the \ion{Fe}{2} profiles show qualitative differences. 
the ISM model.  The \feiid\ resonance transitions each exhibit much
greater absorption at $v \approx 0 \mkms$ than the fiducial model.
The resonant line-emission is also substantially
reduced, implying much higher fluxes for the non-resonant lines (e.g.\
\feiic).  The lack of scattered \feiia\ photons results in an
absorption profile that very nearly matches the input opacity profile.
We conclude that resonance transitions that are strongly coupled to
non-resonant lines offer the best
characterization of an ISM component.
}
\label{fig:ISM_spec}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_ism_ifu.ps}
\caption{
Surface-brightness emission maps for ISM+wind model
}
\label{fig:ISM_ifu}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_vary_profiles.ps}
\caption{
Power-law profiles
}
\label{fig:plaws}
\end{figure}

\begin{figure}
\includegraphics[scale=0.6,angle=90]{Figures/fig_plaw_spec.ps}
\caption{
Power-law profiles spectral lines
}
\label{fig:plaws_spec}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_radiation_nvt.ps}
\caption{
Radiation diagnosed
}
\label{fig:rad_nvt}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_rad_spec.ps}
\caption{
Radiation spec
}
\label{fig:rad_spec}
\end{figure}
